\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhf}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
Austin, TX \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Data Engineer} with expertise in building scalable data pipelines and cloud-based solutions. Skilled in \textbf{Python, AWS services, ETL development, and cloud-native technologies}. Passionate about designing high-performance data architectures and leveraging AI/ML workflows for transformative solutions in the automotive technology domain.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{New York, USA}
{Data Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed scalable \textbf{Python and AWS} data pipelines using \textbf{Airflow, PySpark, and AWS services (ECS, Lambda, SQS, DynamoDB)} to automate data ingestion from diverse sources, reducing manual processing overhead.}
\resumeItem{Implemented real-time streaming infrastructure with \textbf{Kafka and cloud-native technologies}, processing event data with sub-second latency and ensuring high-reliability data delivery.}
\resumeItem{Optimized data storage architectures across \textbf{cloud platforms (AWS S3, Snowflake, AWS Redshift)} using advanced partitioning and compression strategies to improve query performance.}
\resumeItem{Designed and maintained CI/CD workflows using \textbf{Jenkins and AWS CodePipeline}, integrating automated data quality checks and monitoring frameworks to enhance pipeline reliability.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Data Engineer}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Engineered \textbf{PySpark data processing workflows} on \textbf{AWS EMR}, implementing performance optimizations that reduced data transformation execution time by 60\%.}
\resumeItem{Developed serverless data architectures using \textbf{AWS Lambda, API Gateway, and event-driven microservices}, demonstrating expertise in cloud-native application design.}
\resumeItem{Created \textbf{Apache Airflow DAGs} for complex data pipeline orchestration, ensuring robust task dependencies and efficient workflow management.}
\resumeItem{Evaluated and prototyped \textbf{AWS Neptune Graph Database} for advanced data modeling and relationship tracking.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{AWS Data Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Designed and maintained \textbf{AWS data lakes and warehouses} using \textbf{S3, Athena, Snowflake, and Redshift}, implementing strategic data partitioning to optimize query performance.}
\resumeItem{Built robust \textbf{ETL pipelines} using \textbf{PySpark and AWS services}, processing and transforming daily data volumes with comprehensive data quality checks.}
\resumeItem{Implemented \textbf{serverless data ingestion} via \textbf{AWS Lambda and SQS}, creating event-driven architectures that reduced manual pipeline management.}
\resumeItem{Developed automated \textbf{CI/CD pipelines} using \textbf{Jenkins and GitLab Actions} to streamline data pipeline deployment and version control.}
\resumeItemListEnd

\resumeSubheading{Catalog}{India}
{Machine Learning Intern}{Jan 2021 -- Jun 2021}
\resumeItemListStart
\resumeItem{Leveraged \textbf{PySpark for distributed data analysis} on blockchain datasets, demonstrating scalable data processing capabilities.}
\resumeItem{Developed \textbf{Python and SQL ETL pipelines} for preprocessing complex blockchain transaction data, preparing datasets for machine learning workflows.}
\resumeItem{Automated ML model training and deployment using \textbf{Apache Airflow DAGs} and \textbf{FastAPI microservices}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & Python, SQL, R \\
\textbf{Cloud \& DevOps:} & \textbf{AWS (EMR, S3, Lambda, ECS, SQS, DynamoDB)}, Snowflake, Docker, Kubernetes, Git, CI/CD \\
\textbf{Data Engineering:} & Apache Airflow, PySpark, ETL/ELT, Kafka, \textbf{Vector Databases}, MLOps \\
\textbf{Databases:} & PostgreSQL, MySQL, MongoDB, \textbf{AWS Neptune Graph Database} \\
\textbf{AI/ML Tools:} & scikit-learn, PyTorch, GitHub Copilot, MLflow
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{AI-Powered Data Preprocessing Framework}{Python, AWS, MLOps}
\resumeItemListStart
\resumeItem{Developed an end-to-end \textbf{AI data preparation pipeline} focusing on automated feature engineering and data quality assessment using \textbf{vector databases and prompt engineering}.}
\resumeItem{Implemented \textbf{MLOps practices} with automated model monitoring, versioning, and deployment using \textbf{GitHub Actions and MLflow}, ensuring reproducible machine learning workflows.}
\resumeItem{Created intelligent data cleaning module using \textbf{AI-assisted development tools} that reduced manual data preprocessing time by 40\%.}
\resumeItem{Designed serverless architecture on \textbf{AWS Lambda} for scalable data transformation, processing 10K+ records with sub-second latency.}
\resumeItemListEnd

\resumeProjectHeading{Microservices Communication Framework}{Go, gRPC, Docker, Kubernetes}
\resumeItemListStart
\resumeItem{Architected resilient microservices with \textbf{gRPC}, implementing advanced networking patterns like circuit breakers and retry policies.}
\resumeItem{Built comprehensive observability stack using \textbf{Prometheus, Grafana, and Jaeger} for distributed system monitoring.}
\resumeItem{Automated deployment using \textbf{Docker Compose and Helm charts}, demonstrating cloud-native infrastructure skills.}
\resumeItem{Conducted performance benchmarking, analyzing service mesh overhead and optimizing inter-service communication latency.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}
\resumeSubHeadingListEnd

\end{document}