\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhf}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
Austin, TX 78701 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

\section{Summary}
\textbf{Data Engineer} with expertise in building scalable data pipelines using \textbf{Python, AWS services, and cloud-native technologies}. Passionate about designing high-performance data solutions with strong skills in \textbf{ETL processes, MLOps, and cloud infrastructure}. Proven ability to develop robust data architectures and collaborate effectively in agile environments.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Cox Automotive}{Austin, TX}
{Data Engineer I}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed scalable \textbf{Python-based data pipelines} using \textbf{AWS services} including \textbf{ECS, Lambda, SQS, DynamoDB, and Step Functions} to process diverse automotive industry data sources with high reliability.}
\resumeItem{Implemented \textbf{ETL workflows} in \textbf{Snowflake} and \textbf{NoSQL databases}, designing efficient data models that support real-time analytics and machine learning preprocessing requirements.}
\resumeItem{Collaborated with cross-functional teams to design and deploy data solutions, applying \textbf{object-oriented design patterns} and maintaining robust, maintainable code architecture.}
\resumeItem{Contributed to \textbf{CI/CD operations}, creating automated data quality checks and monitoring frameworks that ensure pipeline integrity and minimize data processing errors.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Data Engineer}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Optimized \textbf{PySpark} financial data workflows on \textbf{AWS EMR}, implementing advanced DataFrame transformations that reduced processing time by 45\% while maintaining data integrity.}
\resumeItem{Developed serverless \textbf{AWS Lambda} APIs with \textbf{API Gateway}, conducting comprehensive load testing to validate scalability and performance of internal data services.}
\resumeItem{Designed \textbf{Apache Airflow} data pipelines with complex task dependencies, ensuring robust workflow management and reliable data processing.}
\resumeItem{Evaluated emerging database technologies like \textbf{AWS Neptune Graph Database} for potential implementation in team's data modeling strategies.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{AWS Data Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Configured \textbf{Amazon S3} data lakes with intelligent partitioning strategies, managing 2-3 TB of structured and semi-structured data with enhanced query performance.}
\resumeItem{Developed \textbf{PySpark ETL pipelines} to transform and enrich daily transactional data from multiple AWS sources, processing 1-5 GB of data with robust data quality checks.}
\resumeItem{Orchestrated \textbf{Airflow DAGs} for automated ETL workflows, implementing sophisticated job dependencies, retry mechanisms, and comprehensive alerting systems.}
\resumeItem{Implemented event-driven data ingestion using \textbf{AWS Lambda} triggers on \textbf{S3} uploads and \textbf{SQS} messages, reducing manual pipeline interventions by 30\%.}
\resumeItemListEnd

\resumeSubheading{Catalog}{India}
{Machine Learning Intern}{Jan 2021 -- Jun 2021}
\resumeItemListStart
\resumeItem{Conducted distributed data analysis using \textbf{PySpark} for scalable machine learning workflows on blockchain transaction datasets.}
\resumeItem{Developed \textbf{Python and SQL ETL pipelines} to preprocess raw blockchain data, enabling effective model training and feature engineering.}
\resumeItem{Automated machine learning workflows using \textbf{Apache Airflow}, creating modular DAGs for model training, evaluation, and deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & Python, SQL \\
\textbf{Cloud \& Data Engineering:} & AWS (S3, Lambda, ECS, SQS, DynamoDB), Snowflake, Airflow, Docker, Kubernetes \\
\textbf{Databases:} & PostgreSQL, MySQL, MongoDB, NoSQL Databases \\
\textbf{Big Data \& ML:} & PySpark, Apache Kafka, MLOps, Vector Databases \\
\textbf{Tools:} & Git, CI/CD, Jenkins, GitHub Copilot
\end{tabularx}

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{AI/ML Data Preparation Pipeline}{Personal Project}
\resumeItemListStart
\resumeItem{Designed end-to-end \textbf{MLOps} pipeline for preparing diverse datasets, implementing automated data validation and transformation using \textbf{Python} and \textbf{Apache Airflow}.}
\resumeItem{Integrated \textbf{vector database} technologies for efficient machine learning model training, demonstrating advanced data preprocessing techniques.}
\resumeItem{Implemented robust \textbf{data governance} practices, ensuring ethical AI data management and comprehensive feature tracking.}
\resumeItem{Developed modular data transformation scripts compatible with various AI model training frameworks like \textbf{PyTorch} and \textbf{TensorFlow}.}
\resumeItemListEnd

\resumeProjectHeading{Microservices Communication Framework}{Personal Project}
\resumeItemListStart
\resumeItem{Architected distributed microservices using \textbf{gRPC}, \textbf{Docker}, and \textbf{Kubernetes}, implementing advanced networking patterns for resilient system design.}
\resumeItem{Established comprehensive observability infrastructure with \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Jaeger} for performance monitoring and tracing.}
\resumeItem{Implemented security features including mutual TLS, circuit breakers, and intelligent request routing.}
\resumeItem{Benchmarked and optimized microservices architecture, quantifying performance improvements and system overhead.}
\resumeItemListEnd

\resumeProjectHeading{Prompt Engineering \& LLM Integration}{Personal Project}
\resumeItemListStart
\resumeItem{Developed experimental framework for evaluating large language model performance using advanced prompting techniques.}
\resumeItem{Implemented custom evaluation metrics and comparative analysis of different prompting strategies.}
\resumeItem{Explored ethical AI practices and potential bias mitigation in language models.}
\resumeItem{Created reproducible research environment using \textbf{Jupyter Notebooks} and version control best practices.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}
\resumeSubHeadingListEnd

\end{document}