\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhf}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Data Engineer} with expertise in data analysis, reporting, and pipeline development for healthcare and insurance domains. Proficient in \textbf{SQL}, \textbf{MS Office}, and \textbf{business intelligence tools} like \textbf{Power BI}, with strong skills in preparing datasets, maintaining data quality, and supporting data-driven decision-making.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{UnitedHealthcare}{Remote, USA}
{Data Analyst / Data Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Prepared and cleaned healthcare datasets using \textbf{SQL} and \textbf{MS Excel}, supporting exploratory data analysis for medical billing and insurance claims data.}
\resumeItem{Developed and maintained data pipelines to organize and filter medical claims data (CPT/DX, NDC codes) for trend identification and reporting needs.}
\resumeItem{Created and enhanced \textbf{Power BI} dashboards to visualize healthcare data, enabling data-driven insights for medical billing and insurance analysis.}
\resumeItem{Implemented data quality checks and maintained reliability of healthcare data systems, ensuring accurate reporting of patient and claims information.}
\resumeItemListEnd

\resumeSubheading{Citi}{NewYork,USA}
{Data Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Designed scalable ETL pipelines using \textbf{SQL} and data manipulation techniques to process and analyze financial datasets with high accuracy.}
\resumeItem{Built data infrastructure to support reporting needs, utilizing business intelligence tools to transform raw data into actionable insights.}
\resumeItem{Collaborated with senior analysts to apply appropriate analytic methods for solving complex business problems in financial data domains.}
\resumeItem{Maintained data documentation and metadata repositories to improve data transparency and usability across financial reporting systems.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Data Engineer}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Developed data pipelines using \textbf{SQL} and reporting tools to support financial data analysis and reporting requirements.}
\resumeItem{Created \textbf{Power BI} dashboards to visualize complex financial datasets, enabling data-driven decision-making.}
\resumeItem{Implemented data quality checks and maintained reliability of financial reporting systems.}
\resumeItem{Supported exploratory data analysis tasks by preparing and cleaning financial datasets.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{Data Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Configured and maintained databases storing insurance and customer data, implementing robust data management strategies.}
\resumeItem{Developed SQL queries for extracting and aggregating insurance policy and customer records with high precision.}
\resumeItem{Created data pipelines to transform and process insurance-related datasets, ensuring data quality and reliability.}
\resumeItem{Implemented reporting solutions using business intelligence tools to support insurance data analysis.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages \& Analytics:} & \textbf{SQL}, Python, R, MS Excel, MS Office \\
\textbf{Business Intelligence:} & \textbf{Power BI}, \textbf{SSRS}, Tableau \\
\textbf{Data Tools:} & Microsoft Access, SQL Server, Oracle \\
\textbf{Domains:} & Medical Billing, Insurance Claims, Healthcare Data Analysis \\
\textbf{Soft Skills:} & Data Cleaning, Reporting, Problem-solving, Analytical Skills
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{Healthcare Claims Analysis Project | SQL, Power BI}{Personal Project}
\resumeItemListStart
\resumeItem{Developed a comprehensive analysis framework for processing medical claims data using \textbf{SQL} and \textbf{Power BI}.}
\resumeItem{Created interactive dashboards visualizing insurance claim patterns, patient demographics, and treatment trends.}
\resumeItem{Implemented data cleaning and transformation techniques to ensure high-quality healthcare data analysis.}
\resumeItem{Demonstrated proficiency in handling medical billing data (CPT/DX codes, NDC) and generating meaningful insights.}
\resumeItemListEnd

\resumeProjectHeading{Insurance Data Pipeline | Python, SQL, Airflow}{Personal Project}
\resumeItemListStart
\resumeItem{Designed an end-to-end data pipeline for processing insurance-related datasets using \textbf{Python} and \textbf{Airflow}.}
\resumeItem{Implemented data extraction, transformation, and loading (ETL) processes for insurance claim records.}
\resumeItem{Developed automated data quality checks and reporting mechanisms to ensure data reliability.}
\resumeItem{Created modular and scalable data processing workflows for insurance data management.}
\resumeItemListEnd

\resumeProjectHeading{Medical Reporting Dashboard | Power BI, SQL}{Personal Project}
\resumeItemListStart
\resumeItem{Built a comprehensive medical reporting dashboard using \textbf{Power BI} and \textbf{SQL}.}
\resumeItem{Integrated multiple data sources to create a unified view of healthcare performance metrics.}
\resumeItem{Implemented advanced data visualization techniques to highlight key healthcare trends and insights.}
\resumeItem{Demonstrated ability to transform complex medical data into actionable business intelligence.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}
\resumeSubHeadingListEnd

\end{document}