\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Software Engineer} with 3+ years of experience designing and developing scalable, user-friendly web applications. Skilled in \textbf{C\#, .NET Core, ASP.NET MVC, EF Core, SQL, React, and Angular}. Proven track record in \textbf{troubleshooting}, \textbf{debugging}, and delivering high-quality software with a strong focus on \textbf{user experience}. Experienced in migrating legacy applications, building \textbf{RESTful APIs}, and utilizing \textbf{Azure DevOps} for CI/CD.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{NewYork,USA}
{Software Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed an \textbf{ASP.NET Core} web application for managing customer support requests, focusing on enhancing user experience, as part of a 4-person team where I served as the technical lead.}
\resumeItem{Designed and built 3 \textbf{RESTful APIs} using \textbf{ASP.NET Core} and \textbf{EF Core}, handling 4,200 daily requests with an average response time of 150ms.}
\resumeItem{Migrated a legacy \textbf{ASP.NET MVC} application to a modern \textbf{Angular} SPA, resulting in a 28\% improvement in page load times and a 19\% reduction in bounce rates.}
\resumeItem{Configured \textbf{Azure DevOps} pipelines for CI/CD and automated deployments, reducing manual effort by 32\% and increasing deployment frequency from weekly to daily.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Data engineer}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Optimized existing PySpark financial processing workflows on AWS EMR by refactoring data structures and implementing DataFrame optimizations, reducing execution time by 60\% while maintaining data integrity
}
\resumeItem{Evaluated AWS Neptune Graph Database feasibility against existing relational implementations, analyzing performance for team workflow data models.}
\resumeItem{Implemented serverless APIs using AWS API Gateway and Lambda functions, while conducting comprehensive load testing for 25+ internal APIs using performance testing tools to validate scalability}
\resumeItem{Developed and maintained data pipelines using Apache Airflow, creating DAGs with proper task dependencies }
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{Associate Software Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Built a \textbf{.NET Core} web portal for managing insurance policies as part of a 3-person team, serving as the primary back-end developer.}
\resumeItem{Implemented a \textbf{React} front-end for the policy management system, integrating with \textbf{RESTful APIs} and reducing page load times by 250ms.}
\resumeItem{Developed and maintained 6 \textbf{ASP.NET MVC} applications, collaborating with cross-functional teams to deliver features based on business requirements.}
\resumeItem{Performed code reviews, wrote unit tests using \textbf{MSTest}, and ensured adherence to coding standards and best practices.}
\resumeItemListEnd
\vspace{-5mm}

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & \textbf{C\#}, Python, SQL, JavaScript, \textbf{HTML}, \textbf{CSS} \\
\textbf{Frameworks \& Libraries:} & \textbf{.NET Core}, \textbf{ASP.NET MVC}, \textbf{EF Core}, \textbf{React}, \textbf{Angular}, Node.js \\
\textbf{Databases:} & \textbf{SQL Server}, PostgreSQL, MongoDB \\
\textbf{Tools \& Platforms:} & \textbf{Azure DevOps}, Git, Docker, \textbf{AWS}, Jenkins, Jira \\
\textbf{Testing:} & \textbf{MSTest}, \textbf{NUnit}, \textbf{xUnit}, Moq, Jasmine, Karma \\
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\textbf{Customer Support Portal | ASP.NET Core, Angular, SQL Server}{}
\resumeItemListStart
\resumeItem{Developed a customer support portal as part of a 2-person team, focusing on improving user self-service capabilities, where I served as the full-stack developer.}
\resumeItem{Built a responsive \textbf{Angular} front-end, integrating with \textbf{ASP.NET Core} \textbf{APIs} and reducing support ticket volume by 18\%.}
\resumeItem{Implemented role-based access control and user authentication using \textbf{OAuth} and \textbf{OpenID Connect}.}
\resumeItem{Optimized database queries and indexes, resulting in a 28\% improvement in average API response times.}
\resumeItemListEnd

\textbf{Insurance Policy Management System | React, ASP.NET Core, EF Core}{}
\resumeItemListStart
\resumeItem{Built a web-based insurance policy management system as the sole developer, focusing on streamlining policy creation and maintenance workflows.}
\resumeItem{Developed a \textbf{React} front-end with reusable components, reducing development time by 25\% for future feature additions.}
\resumeItem{Designed and implemented \textbf{RESTful APIs} using \textbf{ASP.NET Core} and \textbf{EF Core}, handling 2,500 requests per day with an average response time of 180ms.}
\resumeItem{Implemented search functionality using \textbf{Elasticsearch}, enabling users to quickly find policies based on various criteria.}
\resumeItemListEnd

\textbf{Legacy Application Migration | ASP.NET MVC, Angular, Azure DevOps}{}
\resumeItemListStart
\resumeItem{Migrated a legacy \textbf{ASP.NET MVC} application to a modern \textbf{Angular} SPA as part of a 3-person team, where I focused on the front-end development.}
\resumeItem{Refactored the front-end codebase using \textbf{TypeScript} and \textbf{RxJS}, improving code maintainability and reducing bug reports by 32\%.}
\resumeItem{Integrated the \textbf{Angular} front-end with existing \textbf{ASP.NET MVC} controllers and views, ensuring seamless functionality during the migration process.}
\resumeItem{Configured \textbf{Azure DevOps} pipelines for continuous integration and deployment, enabling daily deployments and reducing manual effort by 40\%.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}

\end{document}