Here is the optimized LaTeX resume tailored to the provided job description:

\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
Charlotte, NC \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Software Engineer} with strong \textbf{Python} development skills and 3+ years of experience building and deploying \textbf{scalable systems on AWS}. Proven ability to write clean, modular, object-oriented code and architect robust solutions. Hands-on expertise in \textbf{system design}, \textbf{NoSQL/SQL databases}, \textbf{CI/CD pipelines}, and \textbf{container orchestration}. Passionate about leveraging AI to automate enterprise workflows.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{New York, USA}
{Software Engineer - Automated Underwriting System}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed an \textbf{AI-powered loan underwriting system} as part of a 4-member team, leveraging \textbf{PyTorch}, \textbf{Python}, and \textbf{AWS services} to automate credit decisioning, reducing manual processing time by 60\%.}
\resumeItem{Integrated \textbf{generative AI models} and \textbf{reasoning agents} to analyze applicant data from multiple sources (\textbf{S3}, \textbf{DynamoDB}), extracting key insights for AI-assisted underwriting across 25,000 applications.}
\resumeItem{Designed and deployed a \textbf{scalable microservices architecture} using \textbf{AWS Lambda}, \textbf{API Gateway}, and \textbf{ECS}, enabling the system to process up to 5,000 concurrent requests with sub-second latency.}
\resumeItem{Implemented \textbf{CI/CD pipelines} with \textbf{AWS CodePipeline} and \textbf{CloudFormation} for Infrastructure-as-Code, automating builds, testing, and deployments to production.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Software Development Engineer Intern - Portfolio Analytics Platform}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Built a \textbf{real-time portfolio analytics engine} using \textbf{Python} and \textbf{AWS}, ingesting market data from \textbf{Kafka} streams and calculating risk metrics for 10,000 portfolios with a 3-member team.}
\resumeItem{Developed \textbf{serverless APIs} using \textbf{AWS Lambda} and \textbf{API Gateway}, enabling secure access to analytics results, handling 500 requests per second during peak load.}
\resumeItem{Optimized \textbf{data storage} and retrieval using \textbf{DynamoDB}, reducing query latency by 40\% through index optimizations and caching strategies.}
\resumeItem{Implemented an \textbf{alert system} to notify users of portfolio risk threshold breaches, using \textbf{AWS SNS} and \textbf{Lambda}, ensuring timely insights delivery.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{Software Engineer - Claims Processing Automation}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Developed an \textbf{AI-powered claims processing system} using \textbf{Python}, \textbf{scikit-learn}, and \textbf{AWS}, automating claims validation and routing for 10,000 daily claims.}
\resumeItem{Built \textbf{data pipelines} using \textbf{AWS Glue} and \textbf{S3} to extract, transform, and load claims data from multiple sources, processing 5GB of data per day.}
\resumeItem{Implemented \textbf{machine learning models} to classify and prioritize claims based on complexity and fraud risk, improving processing accuracy by 25\% and reducing manual review time by 40\%.}
\resumeItem{Designed a \textbf{scalable API layer} using \textbf{AWS API Gateway} and \textbf{Lambda} to expose claims processing functionality, supporting 1,000 requests per second.}
\resumeItemListEnd
\vspace{-5mm}

\resumeSubheading{Catalog}{India}
{Machine Learning Intern - Supply Chain Optimization}{Jan 2021 -- Jun 2021}
\resumeItemListStart
\resumeItem{Developed a \textbf{supply chain optimization model} using \textbf{Python} and \textbf{PySpark} to recommend optimal inventory levels and distribution strategies, analyzing 10GB of historical sales and logistics data.}
\resumeItem{Built \textbf{ETL pipelines} using \textbf{Apache Spark} and \textbf{AWS S3} to preprocess and transform supply chain data for machine learning workflows.}
\resumeItem{Deployed the optimization model as a \textbf{scalable API} using \textbf{AWS ECS} and \textbf{Docker}, enabling real-time inventory recommendations for 500 products.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\textbf{Enterprise Workflow Automation Platform | Python, AWS Lambda, ECS, DynamoDB}{}
\resumeItemListStart
\resumeItem{Architected a \textbf{serverless platform} for automating enterprise workflows using \textbf{generative AI} and \textbf{agent-based systems}, leveraging \textbf{AWS Lambda}, \textbf{ECS}, and \textbf{DynamoDB}.}
\resumeItem{Developed \textbf{pluggable AI modules} for document understanding, decision making, and task execution using \textbf{PyTorch}, \textbf{spaCy}, and \textbf{Python}, enabling customizable workflow automation.}
\resumeItem{Designed a \textbf{scalable event-driven architecture} using \textbf{AWS Step Functions} and \textbf{SQS} to orchestrate multi-step workflows, processing up to 10,000 events per day.}
\resumeItem{Implemented a \textbf{user-friendly web interface} using \textbf{React} and \textbf{AWS Amplify} for workflow configuration and monitoring, with \textbf{real-time updates} using \textbf{WebSocket API}.}
\resumeItemListEnd

\textbf{Intelligent Document Processing Pipeline | Python, AWS Textract, Comprehend}{}
\resumeItemStart
\resumeItem{Built an \textbf{intelligent document processing pipeline} to extract, classify, and analyze unstructured data from various document formats (\textbf{PDF}, \textbf{DOCX}, \textbf{images}) using \textbf{AWS Textract} and \textbf{Comprehend}.}
\resumeItem{Developed \textbf{custom entity recognition models} using \textbf{spaCy} and \textbf{AWS SageMaker} to identify domain-specific entities and relationships within documents, achieving 85\% F1 score.}
\resumeItem{Implemented a \textbf{document similarity engine} using \textbf{sentence-transformers} and \textbf{FAISS} to enable fast retrieval of relevant documents based on semantic similarity, supporting 100,000 documents.}
\resumeItem{Deployed the pipeline as a \textbf{serverless API} using \textbf{AWS Lambda} and \textbf{API Gateway}, processing 5,000 documents per day with an average latency of 500ms.}
\resumeItemListEnd

\textbf{Multi-Modal Conversational AI Assistant | Python, PyTorch, AWS Lambda}{}
\resumeItemListStart
\resumeItem{Developed a \textbf{multi-modal conversational AI assistant} capable of engaging in text, speech, and image-based interactions, using \textbf{PyTorch}, \textbf{Hugging Face Transformers}, and \textbf{AWS services}.}
\resumeItem{Fine-tuned \textbf{pre-trained language models} (BERT, GPT-2) on domain-specific data to enable \textbf{contextual understanding} and \textbf{coherent response generation} for user queries.}
\resumeItem{Integrated \textbf{speech recognition} and \textbf{text-to-speech} capabilities using \textbf{AWS Transcribe} and \textbf{Polly}, allowing users to interact with the assistant using voice commands.}
\resumeItem{Implemented \textbf{image understanding} using \textbf{AWS Rekognition} and \textbf{PyTorch} vision models to enable the assistant to analyze and respond to visual inputs, such as product images or user photos.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & \textbf{Python}, Java, JavaScript, SQL \\
\textbf{AWS Services:} & \textbf{Lambda}, \textbf{ECS}, \textbf{S3}, \textbf{DynamoDB}, \textbf{API Gateway}, \textbf{SQS}, \textbf{CloudFormation}, \textbf{Textract}, \textbf{Comprehend}, \textbf{SageMaker} \\
\textbf{Databases:} & \textbf{PostgreSQL}, \textbf{MongoDB}, \textbf{DynamoDB}, ElasticSearch \\
\textbf{AI/ML:} & \textbf{PyTorch}, \textbf{scikit-learn}, \textbf{Hugging Face Transformers}, \textbf{spaCy}, \textbf{sentence-transformers}, \textbf{FAISS} \\
\textbf{DevOps:} & \textbf{Docker}, Kubernetes, \textbf{Jenkins}, \textbf{AWS CodePipeline}, Terraform, Ansible \\
\textbf{Web:} & React, Node.js, HTML, CSS, REST APIs
\end{tabularx}

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}

\end{document}