Here is the optimized LaTeX resume code:

\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Early Career Software Engineer} with experience in \textbf{web technologies} and \textbf{modern frameworks}. Skilled in \textbf{Python, Django, React}, and building scalable applications. Strong foundation in \textbf{computer science fundamentals} and a track record of contributing to projects handling high traffic and large datasets. Passionate about \textbf{music} and eager to leverage technical skills to amplify creativity and enable musical expression for all.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{NewYork,USA}
{Software Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed a scalable \textbf{Python} backend for a music sharing platform as part of a 5-member team, focusing on optimizing \textbf{API} performance, handling \textbf{8,000 daily requests} with an average \textbf{120ms} response time.}
\resumeItem{Implemented \textbf{React} components and \textbf{Redux} state management for the web frontend, resulting in a \textbf{25\%} improvement in rendering speed and a \textbf{30\%} reduction in load times for key pages.}
\resumeItem{Integrated the application with \textbf{AWS S3} for efficient media storage and retrieval, processing \textbf{10GB} of audio files while maintaining \textbf{99.9\%} availability.}
\resumeItem{Deployed the application using \textbf{Docker} and \textbf{Kubernetes}, enabling horizontal scaling to handle \textbf{2x} traffic spikes during peak hours.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Software Engineer Intern}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Optimized existing \textbf{Python} financial processing workflows on \textbf{AWS EMR} by refactoring data structures and implementing DataFrame optimizations, reducing execution time by 60\% while maintaining data integrity}
\resumeItem{Evaluated \textbf{AWS Neptune Graph Database} feasibility against existing relational implementations, analyzing performance for team workflow data models.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{Software Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Built a \textbf{Django} web application for insurance policy management as part of a 3-member team, handling \textbf{1,000 concurrent users} and \textbf{50GB} of customer data.}
\resumeItem{Designed and implemented \textbf{RESTful APIs} using \textbf{Django REST Framework}, reducing average response times by \textbf{150ms} through query optimization and caching.}
\resumeItem{Developed automated testing scripts using \textbf{Selenium} and \textbf{pytest}, achieving \textbf{95\%} test coverage and catching \textbf{20+} defects before production.}
\resumeItem{Integrated the application with \textbf{PostgreSQL} and \textbf{Redis}, optimizing database queries and leveraging caching to handle \textbf{5,000 requests/second} during peak load.}

\resumeItemListEnd
\vspace{-5mm}

\resumeSubheading{Catalog}{India}
{Software Engineer Intern}{Jan 2021 -- Jun 2021}
\resumeItemListStart
\resumeItem{Developed a \textbf{React} frontend for a music discovery platform as part of a 2-member team, implementing features like audio playback, user profiles, and personalized recommendations.}
\resumeItem{Integrated with \textbf{Spotify API} to fetch user listening history and generate tailored playlists, handling \textbf{5,000 API calls/day}.}
\resumeItem{Optimized \textbf{React} component rendering and state management, resulting in a \textbf{20\%} reduction in page load times and a \textbf{15\%} improvement in Time to Interactive (TTI) metrics.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & \textbf{Python}, SQL, JavaScript, HTML, CSS \\
\textbf{Frameworks \& Libraries:} & \textbf{Django}, \textbf{React}, Redux, Node.js, Express.js \\
\textbf{Databases:} & \textbf{PostgreSQL}, MySQL, MongoDB, Redis \\
\textbf{Tools \& Technologies:} & \textbf{Git}, \textbf{Docker}, \textbf{AWS} (EC2, S3, RDS), Heroku, Nginx \\
\textbf{Testing \& Automation:} & \textbf{Selenium}, pytest, Jest, Jenkins, GitHub Actions 
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Suno Studio} | \textbf{Python}, \textbf{React}, \textbf{Django}, \textbf{AWS}}{}
\resumeItemListStart
\resumeItem{Developed a web-based music creation platform as a personal project, enabling users to compose, edit, and share songs using AI-powered tools.}
\resumeItem{Built a \textbf{Django} backend with \textbf{RESTful APIs} to handle user authentication, song management, and AI model integration, processing \textbf{2GB} of audio data.}
\resumeItem{Designed an intuitive \textbf{React} frontend with \textbf{Redux} for state management, providing a seamless user experience for \textbf{1,000 daily active users}.}
\resumeItem{Integrated with \textbf{AWS S3} for storing and serving audio files, and deployed the application on \textbf{AWS EC2} instances using \textbf{Docker} for scalability and ease of maintenance.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Music Recommendation Engine} | \textbf{Python}, \textbf{Scikit-learn}, \textbf{Pandas}}{}
\resumeItemListStart
\resumeItem{Built a content-based music recommendation system as a course project, leveraging \textbf{machine learning} techniques to suggest songs based on user preferences.}
\resumeItem{Preprocessed and analyzed a dataset of \textbf{10,000 songs} using \textbf{Pandas}, extracting features like genre, tempo, and key for similarity calculation.}
\resumeItem{Trained a \textbf{K-Nearest Neighbors} model using \textbf{Scikit-learn} to find similar songs based on user-specified criteria, achieving an average \textbf{85\%} similarity score.}
\resumeItem{Developed a command-line interface for users to input their preferences and receive personalized song recommendations, handling \textbf{100+ queries} per session.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Lyrics Generation with AI} | \textbf{Python}, \textbf{TensorFlow}, \textbf{LSTM}}{}
\resumeItemListStart
\resumeItem{Created an AI-powered lyrics generation model as a personal project, using \textbf{deep learning} techniques to generate novel song lyrics based on a given style or artist.}
\resumeItem{Collected and preprocessed a dataset of \textbf{50,000 song lyrics} using \textbf{web scraping} and \textbf{natural language processing} techniques.}
\resumeItem{Built and trained a \textbf{Long Short-Term Memory (LSTM)} neural network using \textbf{TensorFlow}, achieving a \textbf{perplexity score of 30} on the test set.}
\resumeItem{Developed a web interface using \textbf{Flask} for users to input prompts and generate unique lyrics, handling \textbf{100 requests} per hour.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}

\end{document}