\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Software Engineer} with 3+ years of experience developing robust, scalable systems on \textbf{AWS}. Skilled in \textbf{Python}, \textbf{object-oriented design}, and building \textbf{full-stack applications}. Proven ability to translate complex business requirements into clean, modular code. Experience with \textbf{AI agents} and \textbf{Generative AI} technologies.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{New York, USA}
{Software Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed secure \textbf{full-stack applications} using \textbf{Python}, \textbf{JavaScript}, \textbf{HTML/CSS}, and \textbf{AWS} services to automate key business workflows, reducing manual effort by 50\%.}
\resumeItem{Built \textbf{scalable microservices} using \textbf{AWS ECS}, \textbf{API Gateway} and \textbf{Lambda}, enabling seamless integration with internal systems and partner APIs.}
\resumeItem{Implemented \textbf{IaC solutions} using \textbf{CloudFormation} to automate infrastructure provisioning, reducing deployment time by 40\% and eliminating configuration drift.}
\resumeItem{Leveraged \textbf{AI agents} and \textbf{Generative AI} models to build intelligent systems for automating customer support and internal knowledge management.}
\resumeItem{Utilized \textbf{DynamoDB}, \textbf{S3}, \textbf{SQS}, and other AWS services to build highly available, fault-tolerant applications.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Software Engineer Intern}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Developed \textbf{serverless APIs} using \textbf{AWS API Gateway} and \textbf{Lambda} to support internal applications, enabling real-time data access and reducing latency by 35\%.}
\resumeItem{Implemented \textbf{CI/CD pipelines} using \textbf{AWS CodePipeline} and \textbf{CodeBuild} to automate application builds, testing, and deployments, increasing release frequency by 50\%.}
\resumeItem{Conducted comprehensive load testing using \textbf{AWS CloudWatch} and \textbf{Locust} to validate application performance and scalability under high traffic scenarios.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{Software Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Built \textbf{object-oriented} Python applications to automate data ingestion, validation, and processing for \textbf{ETL pipelines}, reducing manual effort by 60\%.}
\resumeItem{Developed and maintained \textbf{SQL} scripts for data extraction, transformation, and loading across \textbf{AWS RDS}, \textbf{Redshift}, and \textbf{S3}.}
\resumeItem{Implemented \textbf{data quality checks} and alerting using \textbf{AWS Lambda} and \textbf{CloudWatch}, ensuring 99.9\% data accuracy and consistency.}
\resumeItem{Utilized \textbf{AWS Step Functions} to orchestrate complex ETL workflows, improving pipeline reliability and reducing failure recovery time by 50\%.}
\resumeItemListEnd

\resumeSubheading{Catalog}{India}
{Software Engineer Intern}{Jan 2021 -- Jun 2021} 
\resumeItemListStart
\resumeItem{Developed \textbf{Python} scripts to automate data ingestion from blockchain APIs, reducing manual effort by 80\% and enabling real-time analytics.}
\resumeItem{Built and deployed \textbf{machine learning models} using \textbf{scikit-learn} and \textbf{AWS SageMaker} to predict fraudulent transactions, achieving 95\% accuracy.}
\resumeItem{Implemented \textbf{ETL pipelines} using \textbf{AWS Glue} and \textbf{PySpark} to process and store large-scale blockchain data in \textbf{AWS S3} for efficient querying and analysis.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages \& Frameworks:} & Python, JavaScript, HTML/CSS, Django, React, Node.js \\
\textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda, DynamoDB, ECS), Git, Docker, Kubernetes, Terraform \\
\textbf{Databases:} & PostgreSQL, MySQL, MongoDB, AWS RDS, DynamoDB \\ 
\textbf{AI \& ML:} & TensorFlow, PyTorch, Hugging Face, OpenAI, Langchain, Anthropic Claude \\
\textbf{Tools:} & Jira, Confluence, Postman, Jupyter, VS Code
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\textbf{Enterprise Chatbot | Python, AWS Lambda, OpenAI, Anthropic Claude}{}
\resumeItemListStart
\resumeItem{Developed a conversational AI chatbot to automate IT support and HR functions using \textbf{OpenAI GPT-3} and \textbf{Anthropic Claude} models.}
\resumeItem{Utilized \textbf{AWS Lambda} and \textbf{API Gateway} to build a scalable, serverless backend for handling user requests and integrating with enterprise systems.} 
\resumeItem{Achieved 90\% accuracy in answering common employee queries, reducing support ticket volume by 50\% and improving response times by 70\%.}
\resumeItemListEnd

\textbf{Fraud Detection Platform | Python, AWS SageMaker, DynamoDB}{}
\resumeItemListStart
\resumeItem{Built a real-time fraud detection platform for financial transactions using \textbf{machine learning models} trained on \textbf{AWS SageMaker}.}
\resumeItem{Implemented feature engineering pipelines using \textbf{PySpark} and \textbf{AWS Glue} to process and transform large-scale transactional data.}
\resumeItem{Utilized \textbf{AWS DynamoDB} for low-latency storage and retrieval of model predictions, enabling sub-second response times for fraud scoring.}
\resumeItem{Achieved 95\% precision in identifying fraudulent transactions, saving the company \$2M+ in potential losses annually.} 
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}

\resumeSubHeadingListEnd

\end{document}