\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Data Scientist / Analytics Engineer} with 3+ years experience across \textbf{analytics, engineering, and BI}. Skilled in \textbf{dbt, Python, BigQuery, and data modeling}. Proven track record of scaling analytics, optimizing dbt pipelines, and partnering with stakeholders to enable data-driven decisions.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{NewYork,USA}
{Data Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed \textbf{dbt semantic layer}, defining 40+ metrics to standardize definitions and enabling self-service analytics across the company.}
\resumeItem{Optimized \textbf{BigQuery performance and costs} using partitioning, clustering, and incremental models; reduced query times by 30\% and costs by 20\% for key dbt models.}
\resumeItem{Built \textbf{CI/CD pipeline for dbt} using dbt Cloud, leveraging testing, documentation, and Slack alerts to ensure trusted analytics.}
\resumeItem{Designed \textbf{product analytics} schemas and pipelines to track user funnels, retention, and engagement; data used to improve onboarding and reduce churn.}
\resumeItem{Partnered with business stakeholders to translate requirements into technical specifications; built 15+ new dbt models to power marketing and growth initiatives.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Data engineer}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Orchestrated complex ETL workflows using \textbf{Airflow DAGs} with dynamic task generation and dependencies; supported 10+ business processes.}
\resumeItem{Built \textbf{data quality framework} with dbt tests, data freshness checks, and anomaly detection to monitor 20+ critical datasets.}
\resumeItem{Partnered with data scientists to develop analytics-ready feature sets; improved model performance by 15\% through better feature engineering.}
\resumeItem{Automated financial reporting using dbt and Tableau, saving 20+ hours per month of manual work.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{AWS Data Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Developed \textbf{end-to-end analytics platform} on AWS using S3, Glue, Athena, and QuickSight; unified \textbf{siloed datasets} for 360-degree customer view.}
\resumeItem{Designed \textbf{data lake} architecture on S3 for \textbf{2+ PB} of structured and semi-structured data; enabled analytics at scale.}
\resumeItem{Built \textbf{50+ ETL jobs} using AWS Glue and Python to transform and enrich data from 10+ sources; supported analytics for claims, policies, and customer 360.}
\resumeItem{Created \textbf{metadata-driven ELT framework} to automate Glue job generation; reduced development time by 40\% and enabled easy onboarding of new data sources.}
\resumeItem{Optimized \textbf{S3 partitioning and compression} schemes; reduced Athena query costs by 30\% and improved performance by 2x.}
\resumeItemListEnd
\vspace{-5mm}

\resumeSubheading{Catalog}{India}
{Machine Learning Intern}{Jan 2021 -- Jun 2021}
\resumeItemListStart
\resumeItem{Built recommendation engine for ecommerce products using collaborative filtering in \textbf{PySpark} on AWS EMR.}
\resumeItem{Developed \textbf{streaming ETL pipeline} using Kinesis and Lambda to process clickstream events; enabled real-time personalization.}
\resumeItem{Created \textbf{product analytics dashboards} in QuickSight to track user engagement, revenue, and conversion metrics.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Analytics Engineering:} & dbt (core \& Cloud), SQL, BigQuery, Snowflake, Redshift \\
\textbf{Data Orchestration:} & Airflow, Dagster, CI/CD pipelines, Great Expectations\\
\textbf{Cloud \& Data Platforms:} & AWS (S3, Glue, Athena, Lambda), GCP (BigQuery, Composer, Dataflow) \\
\textbf{BI \& Visualization:} & Tableau, QuickSight, Data Studio, Looker \\
\textbf{Programming:} & Python, Spark (PySpark), Git, Bash
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\textbf{Semantic Analytics Layer | dbt, BigQuery, Looker}{}
\resumeItemListStart
\resumeItem{Led development of \textbf{dbt semantic layer} at enterprise scale with 100+ well-defined metrics; partnered with finance, marketing, and product teams to align definitions.}
\resumeItem{Architected \textbf{modular dbt project} structure for easy collaboration; built \textbf{CI/CD workflows} and \textbf{data quality tests} to ensure accuracy and reliability.}
\resumeItem{Optimized \textbf{BigQuery costs and performance} through clustering, incremental models, and smart materializations; \textbf{reduced pipeline run time by 40\%}.}
\resumeItem{Enabled self-service insights for 200+ business users through \textbf{Looker dashboards} and \textbf{semantic metrics}; \textbf{improved data trust and adoption by 3x}.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}
\resumeSubHeadingListEnd

\end{document}