\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Backend Software Engineer} with expertise in building scalable, distributed systems and delightful user-facing features. Passionate about designing robust REST APIs and developing maintainable backend solutions using \textbf{Golang, Java, and distributed systems technologies}. Proven ability to architect and launch greenfield features from inception to implementation, with a strong focus on performance, reliability, and cross-functional collaboration.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Glean}{New York, USA}
{Backend Software Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed and launched scalable backend features for the Work AI platform, architecting \textbf{REST APIs} with \textbf{Golang} that maximize web client flexibility and support enterprise knowledge graph capabilities.}
\resumeItem{Designed distributed system components leveraging microservices architecture, implementing efficient \textbf{CRUD functionality} across both SQL and NoSQL databases to support Glean's enterprise search and AI assistant infrastructure.}
\resumeItem{Collaborated closely with cross-functional teams including product managers, designers, and data scientists to translate complex requirements into elegant, user-centric technical solutions.}
\resumeItem{Implemented robust testing and monitoring frameworks to ensure API reliability, performance, and seamless integration across Glean's enterprise SaaS connectors.}
\resumeItemListEnd

\resumeSubheading{Citi}{New York, USA}
{Data Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Engineered scalable ETL pipelines using \textbf{Airflow, PySpark, and AWS services}, automating data ingestion from multiple sources and reducing manual processing complexity.}
\resumeItem{Developed real-time streaming infrastructure with \textbf{Kafka} and \textbf{Zookeeper}, processing complex event streams with high reliability and low-latency performance.}
\resumeItem{Optimized data storage strategies across cloud platforms, implementing advanced partitioning and compression techniques to enhance query performance and reduce infrastructure costs.}
\resumeItem{Implemented CI/CD and monitoring frameworks using \textbf{Jenkins} and \textbf{AWS CodePipeline}, introducing automated data quality checks that significantly improved pipeline reliability.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Data Engineer}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Optimized \textbf{PySpark} financial processing workflows on \textbf{AWS EMR}, implementing advanced DataFrame optimizations that reduced execution time while maintaining data integrity.}
\resumeItem{Architected serverless API solutions using \textbf{AWS API Gateway} and \textbf{Lambda functions}, conducting comprehensive load testing to validate scalability and performance.}
\resumeItem{Evaluated and prototyped graph database solutions using \textbf{AWS Neptune}, analyzing performance characteristics for complex workflow data models.}
\resumeItem{Developed data pipeline automation using \textbf{Apache Airflow}, creating sophisticated DAGs with robust task dependencies and error handling.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{AWS Data Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Configured and maintained \textbf{Amazon S3} data storage infrastructure, implementing advanced partitioning strategies that improved query performance in \textbf{AWS Athena}.}
\resumeItem{Developed robust \textbf{PySpark ETL pipelines} for transforming and enriching transactional data across multiple AWS sources, ensuring high data quality and consistency.}
\resumeItem{Implemented event-driven data ingestion using \textbf{AWS Lambda} and \textbf{SQS}, reducing manual pipeline interventions and increasing automation efficiency.}
\resumeItem{Deployed data engineering workflows through automated \textbf{CI/CD pipelines} using \textbf{Jenkins} and \textbf{GitLab Actions}, streamlining deployment processes.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & \textbf{Golang}, \textbf{Java}, Python, SQL \\
\textbf{Backend \& APIs:} & REST APIs, gRPC, OpenAPI, Microservices Architecture \\
\textbf{Cloud \& Infrastructure:} & AWS (S3, Lambda, EMR, API Gateway), Kubernetes, Docker \\
\textbf{Databases:} & SQL, NoSQL, AWS Neptune, Snowflake, Redshift \\
\textbf{Tools \& Frameworks:} & Apache Airflow, Jenkins, GitLab CI/CD, Kafka, Zookeeper \\
\textbf{Data Engineering:} & PySpark, ETL, Data Pipelines, Distributed Systems
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{Enterprise Work AI Microservices Framework}{Personal Project}
\resumeItemListStart
\resumeItem{Designed a scalable microservices communication framework using \textbf{Golang}, \textbf{gRPC}, and \textbf{Kubernetes}, implementing advanced service mesh patterns for enterprise-grade reliability.}
\resumeItem{Implemented mutual TLS (mTLS), circuit breakers, and sophisticated retry policies to ensure robust inter-service communication and fault tolerance.}
\resumeItem{Built comprehensive observability infrastructure using \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Jaeger}, enabling deep performance insights and distributed tracing.}
\resumeItem{Automated deployment with \textbf{Docker Compose} and \textbf{Helm charts}, demonstrating infrastructure-as-code principles and facilitating seamless scalability.}
\resumeItemListEnd

\resumeProjectHeading{Distributed Knowledge Graph Prototype}{Academic Project}
\resumeItemListStart
\resumeItem{Developed a proof-of-concept knowledge graph system using \textbf{Golang} and \textbf{AWS Neptune}, exploring advanced graph database techniques for enterprise knowledge management.}
\resumeItem{Implemented efficient graph traversal and query optimization strategies, processing complex relationship mappings with sub-millisecond latency.}
\resumeItem{Created a modular, extensible architecture supporting multiple data ingestion methods and flexible schema evolution.}
\resumeItem{Demonstrated advanced graph database capabilities through practical implementation of entity resolution and semantic relationship detection.}
\resumeItemListEnd

\resumeProjectHeading{Real-time Event Processing System}{Personal Project}
\resumeItemListStart
\resumeItem{Architected a high-performance event streaming platform using \textbf{Golang}, \textbf{Kafka}, and \textbf{Kubernetes}, capable of processing 5,000 events per second with minimal latency.}
\resumeItem{Implemented sophisticated event routing and transformation logic, showcasing advanced distributed systems design principles.}
\resumeItem{Developed comprehensive monitoring and alerting mechanisms using \textbf{Prometheus} and \textbf{Grafana} for real-time system observability.}
\resumeItem{Achieved 99.99\% system reliability through intelligent failure recovery and graceful degradation strategies.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}
\resumeSubHeadingListEnd

\end{document}