\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------
\newcommand{\resumeItem}[1]{
\begin{tabularx}{\linewidth}{@{}lX@{}}
\raisebox{0.25ex}{\tiny\textbullet} & \small #1 \\
\end{tabularx}
}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
{\small #3} & {\small #4} \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{\item
\begin{tabularx}{\linewidth}{@{}X@{\hfill}r@{}}
\textbf{#1} & #2 \\
\end{tabularx}
\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Document
%-------------------------
\begin{document}

%-----------Header-----------
\begin{center}
{\Huge \scshape Dharama Teja Samudrala} \\ \vspace{2pt} 
New York, NY 14221 \\ \vspace{2pt}
\small
+18573983456 $|$ \href{mailto:dharmatejas102@gmail.com}{dharmatejas102@gmail.com} $|$ 
\href{https://www.linkedin.com/in/dharmatejasamudrala/}{linkedin} $|$ 
\href{https://github.com/dharmateja03}{github}
\end{center}

%-----------Summary-----------
\section{Summary}
\textbf{Full Stack Software Engineer} with \textbf{3+ years} experience building scalable and resilient \textbf{cloud-based applications}. Skilled in \textbf{JavaScript, Java, TypeScript, Python}, and \textbf{Go}. Proven ability to collaborate across Agile teams to deliver robust solutions leveraging \textbf{AWS}, \textbf{open source frameworks}, and \textbf{container orchestration} services. Passionate about staying current with tech trends and mentoring fellow engineers.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Citi}{NewYork,USA}
{Software Engineer}{March 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed a \textbf{microservices-based} banking application as part of a \textbf{5-member team}, focusing on \textbf{real-time transaction processing}, where I served as the \textbf{backend lead}, handling 12,000 requests per day.}
\resumeItem{Implemented \textbf{event-driven architecture} using \textbf{Kafka} and \textbf{AWS Lambda}, reducing transaction latency from 400ms to 150ms and ensuring 99.99\% reliability.}
\resumeItem{Designed and deployed \textbf{CI/CD pipelines} using \textbf{Jenkins} and \textbf{AWS CodePipeline}, automating builds, tests, and deployments, cutting release cycles from 2 weeks to 3 days.}
\resumeItem{Mentored 2 junior developers in \textbf{Agile best practices} and \textbf{software design patterns}, improving team velocity by 20\% and code quality by 30\%.}
\resumeItemListEnd

\resumeSubheading{Fidelity Investments}{Raleigh, NC, USA}
{Software Engineer Intern}{Jun 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Optimized existing \textbf{Java} financial processing workflows by refactoring data structures and algorithms, reducing execution time by 25\% while maintaining 100\% accuracy.}
\resumeItem{Developed and deployed a \textbf{Python}-based \textbf{ETL pipeline} on \textbf{AWS} for ingesting and transforming 10GB of daily trading data, ensuring 99.9\% data quality and availability.}
\resumeItem{Evaluated \textbf{AWS Neptune Graph Database} feasibility against existing relational implementations, analyzing performance for team workflow data models.}
\resumeItem{Implemented \textbf{serverless APIs} using \textbf{AWS API Gateway} and \textbf{Lambda functions}, while conducting comprehensive load testing for 25+ internal APIs using \textbf{JMeter}, validating scalability.}
\resumeItemListEnd

\resumeSubheading{MetLife}{India}
{Software Engineer}{Dec 2021 -- Jul 2023}
\resumeItemListStart
\resumeItem{Built a \textbf{full-stack web application} for managing insurance policies using \textbf{React}, \textbf{Node.js}, and \textbf{PostgreSQL}, processing 25GB of policy data and serving 10,000 users.}
\resumeItem{Developed \textbf{RESTful APIs} using \textbf{Express.js} and integrated with frontend via \textbf{Axios}, ensuring \textbf{CRUD} functionality with 250ms response times.}
\resumeItem{Implemented \textbf{user authentication} and \textbf{authorization} using \textbf{JWT} and \textbf{OAuth 2.0}, securing sensitive customer data and meeting \textbf{HIPAA} compliance.}
\resumeItem{Optimized \textbf{database queries} and introduced \textbf{indexing} strategies, reducing query execution time by 40\% and improving application performance.}
\resumeItemListEnd
\vspace{-5mm}

\resumeSubheading{Catalog}{India}
{Software Engineering Intern}{Jan 2021 -- Jun 2021}
\resumeItemListStart
\resumeItem{Developed a \textbf{React Native} mobile app for tracking product inventory, integrating with \textbf{Firebase} backend and \textbf{Redux} for state management.}
\resumeItem{Implemented \textbf{barcode scanning} functionality using \textbf{react-native-camera}, enabling real-time product lookup and reducing manual entry time by 80\%.}
\resumeItem{Utilized \textbf{Agile methodologies} and participated in \textbf{scrum meetings}, delivering features on-time and collaborating effectively with cross-functional teams.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Languages:} & \textbf{JavaScript, Java, TypeScript, Python, Go, SQL}, HTML/CSS \\
\textbf{Frameworks \& Libraries:} & \textbf{React, Node.js, Express.js, Spring Boot, Django, Flask} \\
\textbf{Databases:} & \textbf{PostgreSQL, MongoDB, AWS RDS, Firebase, AWS Neptune} \\
\textbf{Cloud \& DevOps:} & \textbf{AWS (EC2, S3, Lambda, API Gateway), Docker, Kubernetes, Jenkins, Git} \\
\textbf{Tools \& Methodologies:} & \textbf{Agile, Scrum, Jira, Postman, JMeter, OAuth, JWT} 
\end{tabularx}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
\textbf{E-commerce Platform | React, Node.js, MongoDB, AWS}{}
\resumeItemListStart
\resumeItem{Developed a \textbf{full-stack e-commerce platform} as a \textbf{solo project}, focusing on \textbf{scalability} and \textbf{performance}, handling 5,000 concurrent users.}
\resumeItem{Built \textbf{responsive UI} using \textbf{React} and \textbf{Material-UI}, optimizing for \textbf{cross-device compatibility} and achieving a \textbf{PageSpeed} score of 95.}
\resumeItem{Implemented \textbf{RESTful APIs} using \textbf{Node.js} and \textbf{Express}, integrating with \textbf{MongoDB Atlas} for efficient data storage and retrieval.}
\resumeItem{Deployed on \textbf{AWS EC2} instances with \textbf{load balancing} and \textbf{auto-scaling}, ensuring 99.9\% availability and \textbf{sub-second response times}.}
\resumeItemListEnd

\textbf{Real-time Chat Application | React, Socket.io, Node.js, Firebase}{}
\resumeItemListStart
\resumeItem{Built a \textbf{real-time chat application} as part of a \textbf{2-member team}, focusing on \textbf{instant messaging} and \textbf{presence detection}.}
\resumeItem{Developed \textbf{frontend} using \textbf{React} and integrated \textbf{Socket.io} for \textbf{real-time, bidirectional communication} between client and server.}
\resumeItem{Implemented \textbf{backend} using \textbf{Node.js} and \textbf{Express}, handling \textbf{WebSocket connections} and \textbf{broadcasting messages} to connected clients.}
\resumeItem{Utilized \textbf{Firebase Realtime Database} for storing chat history and user metadata, enabling seamless \textbf{data synchronization} across devices.}
\resumeItemListEnd

\textbf{Microservices Communication Framework | Go, gRPC, Docker, Kubernetes}{}
\resumeItemListStart
\resumeItem{Architected \textbf{3 gRPC microservices} (User, Order, Payment) with \textbf{Envoy sidecar proxies}; implemented \textbf{mTLS}, \textbf{circuit breakers}, and \textbf{retry policies} for resilient inter-service communication.}
\resumeItem{Built \textbf{observability pipeline} using \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Jaeger}; automated deployment with \textbf{Docker Compose} and \textbf{Helm charts}; benchmarked latency across 50,000 requests.}
\resumeItem{Reduced \textbf{P99 latency} by 30\% via \textbf{load balancing}; \textbf{canary routing} cut deployment risk by 40\%; service mesh overhead quantified at 8\% for informed adoption decisions.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rochester Institute Of Technology}{Rochester, NY, USA}
{Master of Science in Computer Science}{Aug 2023 -- Aug 2025}
\resumeSubHeadingListEnd

\end{document}